NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-06-19 paper/itemizedReviewResponse.tex

A: these errors have been fixed.

------------------------------- Reviewer 3 -------------------------------

Q20, After the teaser image, the paper spends the first four pages on neural networks, NLP, and inference. One has to look hard to detect the lede in the next to last paragraph of the introduction ("Moreover, we propose...") Highlight it!

A: We have revise the last paragraph of the introduction to highlight the visualization contributions. The text following "Moreover, we propose..." is not the only place describe visualization contributions, the integrated model pipeline that allow user perturbation in all stages is another contribution, the same holds for the visual encoding for the prediction for the NLI problem.

@@

Q21, Even as a visualization-centric researcher who is aware of NNs and has done a little direct work in NLP, I found it hard to connect to the organization and balance of coverage of these topics in the paper. Despite the prominent teaser visualization and the description of individual views in section 5, the paper comes off as very visualization-light.

A: We appreciated the reviewer concern as organizing a visualization paper for a domain specific application is a very challenge task. The rational for our current orgnaiziation is that the NLP background provides the minimally necessary information for the average reader to understand the application problem. It is an essential part of the paper which make it self-contained. In addition, a lot of the technical details is directly connected to how the visualization encoding is designed (such as the attention view and prediction view). Without a highlevel understanding of the model, it would be impossible for the reader to understand the purpose of most views and the application senarios. Finally, we also try to compress the background information, we spend less than one page on the background, even through other sections mentioned NLP related topics but they mostly still focus on presenting the visualization system.

@@

* How does one handle very different sentence lengths in the sentence view?

A:

* What if the sentence structures between premise and hypothesis are not drastically different; will the matrix be as effective, and thus the graph need to be focused on?

A: The biggest benefit of the graph is the ability for the domain expert to directly see the connection between words. In the matrix, one need to first identify the high value entry and then finding the corresponding row and column to identify the words. If there are multiple correspondence, the user need to check one by one.

@@

* In the pipeline view, doesn't the formulation to approximate the assigned label introduce another black box that the user need to factor into their analytic thinking?

A:

* Why a treemap in the summary view? It's just a 3x3 set of quantities. A simple 3x3 matrix heatmap would be more familiar, more readable, and assure that all of the prediction/label combinations are large enough to select easily.

A: We agree that a 3x3 heatmap (confusion matrix) is also an efficient alternative to represent the summary prediction result. The motivation is use treemap is that it provides a more direct encoding for conveying the count (area instead of variation of colors). And the separate between orange and green tile intuitively convey the correct and incorrect predictions. However, we do think a confusion matrix like encoding could also be beneficial. In the future, we plan to add the confusion matrix as an alternative, so the user can use either one of them based on their preference.

@@

* The description of interaction for the E/E category in the summary view says what one can do, but it's not clear how or why.

A:

Q24, Part of the problem is that the language is very dense in this paper. Although the grammar is acceptable, it was a slow read and there were some passages that I found all but indecipherable, such as the figure 7 caption, the last paragraph of section 5.5, and the bullet list at the end of the introduction.

A: These sections has been revised to improve the readability.

@@

Q25, There were many small errors that need correcting, too many to bother listing here. There was also some hyperbole ("stunning", "unprecedented", "vision", "paradigm") that distracts me as a serious reader and should be replaced. A thorough copyediting should fix both issues.

A: We remove/replace the words mentioned by the reviewer. For example, the following is the updated first sentence of the introduction in which "stunning", "unprecedented" are removed. "Demonstrated by many recent successes, neural networks based machine learning approaches have garnered increasing popularity, and have been adopted in a wide variety of applications."

Q26, The application scenarios in section 6 look useful taken individually, but I wonder about how they are used in combination. The scenarios essentially describe individual tasks that experts might perform in individual views. Scenario 4 goes a little further, but is brief. The paper would very much benefit from a more complete example story of how an analyst might work with the various views in concert to perform higher-level activities. For an application paper like this, some sense of those activities, and how well the tool design works for them, is needed. The last couple paragraphs of section 7 offers only a glimpse of "interrogation" as the authors say.
Their conclusion (participants believe it convenient) isn't sufficiently supported. As it stands, there isn't clear justification of the many visualization design choices. A longer scenario encompassing the larger process would go a long way toward rectifying that.

A: These different senarios should naturally arise during the exploration session, the senarios 1 is often the first step to identify the sentence pair of interests (the user can also manually type the one they interested in senarios 6).

@@

Q27, The supplemental materials are okay. The video should be editing to speed up the (slow!) interactions and preferably include audio.

A: We have revised the video and include voice over and an simple introduction in the begninning.

### 2018-06-19 paper/intro.tex
update intro

Here, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model. Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment. By employing a perturbation-driven paradigm, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.

@@

In summary, the key contributions of this paper are:
\begin{itemize}
  % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
    \item A perturbation-driven exploration paradigm derived from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;

    \item The NLIZE system that enriches such a paradigm by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback; 
    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
    %\item Perform error analysis by examining the stability of the predictions under perturbation;

>>>>

Here, we aim to provide immediate and informative answers to these \emph{``what if''} questions by combining the expressive power of visualization and direct online query/optimization of the neural network model. Instead of viewing the models as invariant objects, we approach the interpretability challenge by studying them in a dynamic environment. By employing a perturbation-driven scheme, we probe the internal states of the model and examine how changes in one part of the pipeline (the input, internal states, and output prediction, see Fig.~\ref{fig:modelPipeline}) affect others, which in turn provides a new perspective to address the model interpretation problem.

@@

In summary, the key contributions of this paper are:
\begin{itemize}
  % \item Distill the visualization tasks for making sense of the role of attention in natural language inference (section~\ref{sec:task});
    \item A perturbation-driven exploration scheme derived from close examination of how domain experts conduct exploratory analysis on end-to-end NLP neural network models;

    \item The NLIZE system that implements the perturbation exploration scheme by providing an intuitive environment that allows domain experts to readily express hypotheses and obtain instantaneous feedback;
    %to  experiment with the intricate relationships among input sentences, model internals, and the prediction;
    %\item Perform error analysis by examining the stability of the predictions under perturbation;
